---
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(cluster)
library(factoextra)
```

## Instruksi

Dataset: Iris Task:

```{r}
# Import data iris
data(iris)

# Remove 'label' so that will impress as unlabeled
df <- cbind(iris$Sepal.Length, iris$Sepal.Width, iris$Petal.Length, iris$Petal.Width)
```

```{r}
# Load PCA from df
pca_iris = prcomp(df, center = TRUE, scale = TRUE) 
```

```{r}
# See summary model PCA to figured out eigenvalue 1 and 2
summary(pca_iris)
```

```{r}
# load for eigenvalue 1 dan 2
pca_iris$sdev^2
```

```{r} 
# load for eigenvector
pca_iris$rotation
```

```{r}
pca_iris$x
```

```{r}
# reduce iris data so will have two columns only
iris_transform = as.data.frame(-pca_iris$x[,1:2])
iris_transform
```

```{r}
# Evaluate k-means towards iris_transform
fviz_nbclust(iris_transform, kmeans, method = 'wss')
fviz_nbclust(iris_transform, kmeans, method = 'silhouette')
```

```{r}
# The best K
k = 2
  
# Visualize k-means clustering on the reduced Iris data
kmeans_iris = kmeans(iris_transform, centers = k, nstart = 50)
fviz_cluster(kmeans_iris, data = iris_transform)
```

## Insight 


a\. Eigenvalues 1 and 2 of the Iris dataset are: 2.918 and 0.914

b\. Based on the summary, it can be seen that 95.81% of the information
contained in the data can be extracted with only 2 Principal
Components. From 4 columns of data, it is reduced to only 2 columns. Size
reduced by 50%, but the information contained only decreased by 4.19%

c\. The optimal 'k' value based on the Elbow and Silhouette method is k = 2
